\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-11-28 projects/project_5/molecular_dynamics/article/article.tex
getting started on diffusion

@@

\listoffigures

>>>>

    In order to compute the \emph{mean square displacement} in section
    \ref{sub:melting_temperature_of_system} we need to keep track of the
    initial position of each atom. We therefore introduce a variable
    \texttt{m\_initialPosition} in the \texttt{Atom-class} which is set during
    initialization.  When computing the diffusion constant $D$, we need to make
    sure that $r_i^2(t)$ is the true displacement, and not the displacement
    relative to the nearest periodic image. This will be implemented in the
    \texttt{applyBoundaryConditions}-method.

@@

In order to measure the melting temperature of the system, we can use the Einstein relation which states the following:
\begin{equation}
    \notag
    \langle r^2(t) \rangle = 6Dt.
\end{equation}
$D$ is here the diffusion constant, $t$ is time and the \emph{mean square displacement} is calculated as
\begin{equation}
    \notag
    r_i^2(t) = \left| \vec{r}_i(t) - \vec{r}_i(0) \right|^2.
\end{equation}
\listoffigures
